Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-07 Moltres.tex
re-export of bib"

Molten salt reactor concepts garnered considerable interest in the 1950s and 60s
with development of the \gls{ARE} and later the \gls{MSRE} at \gls{ORNL}.  With
the inclusion of the \gls{MSR} among the Generation-IV reactor designs
\cite{gif_generation_2008,gif_generation_2015}, this reactor concept has gained renewed research
interest in the past decade, with many new nuclear companies proposing both
fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
\cite{hyde_liquid_2015,leblanc_integral_2015,thorcon_-able_2017,scarlat_design_2014,transatomic_neutronics_2016}. Two
key advantages offered by the fluid-fuelled \gls{MSR} are improved fuel
utilization and no radiation damage constraint on attainable fuel
burn-up. Together, these attributes result in significantly reduced core fissile
inventories and spent nuclear fuel mass 
\cite{gif_generation_2008,gif_generation_2015}.  
Due to these characteristics, the \gls{MSR} is potentially uniquely capable of 
burning actinides and extending fuel resources.

@@

The present work introduces the open source simulation tool, Moltres
\cite{lindsay_arfc/moltres_nodate}, for simulating \glspl{MSR}.  By implementing
deterministic neutronics and thermal hydraulics in the context of the
\gls{MOOSE} finite element modeling framework, Moltres solves arbitrary-group
neutron diffusion, temperature, and precursor governing equations in anywhere
from one to three dimensions and can be deployed on an arbitrary number of
processing units. Through its computing power, Moltres is devoted to previously
unmatched fidelity in coupled neutronics and thermal hydraulics \gls{MSR}
simulation.

@@

Moltres \cite{lindsay_arfc/moltres_nodate} is implemented as an application for
use atop the \gls{MOOSE} \cite{gaston_physics-based_2015} framework.
Accordingly, Moltres includes physics kernels and boundary conditions for
solving for neutron fluxes, temperature, and precursor concentrations. In \gls{MOOSE}
jargon, kernels are C++ classes that contain methods for computing residual and
Jacobian contributions corresponding to individual pieces of governing
equations. Developing the code-base in this way allows modular construction
of equation systems; e.g. the kernel used to represent heat
conduction can also represent generic chemical diffusion. Moltres
also features neutron and precursor ``actions.'' These actions automatically 
construct the systems of equations for an arbitrary number of neutron and
precursor groups. Therefore, as long as group constants are provided in an appropriate
tabular form, a user only has to modify a couple of lines in a Moltres input
file to change from say two to forty-four neutron groups.

>>>>

Molten salt reactor concepts garnered considerable interest in the 1950s and 60s
with development of the \gls{ARE} and later the \gls{MSRE} at \gls{ORNL}.  With
the inclusion of the \gls{MSR} among the Generation-IV reactor designs
\cite{gif_generation_2008,gif_generation_2015}, this reactor concept has gained renewed research
interest in the past decade, with many new nuclear companies proposing both
fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
\cite{hyde_liquid_2015,leblanc_integral_2015,thorcon_-able_2017,scarlat_design_2014,transatomic_power_corporation_neutronics_2016}. 
Two key advantages offered by the fluid-fuelled \gls{MSR} are improved fuel
utilization and no radiation damage constraint on attainable fuel
burn-up. Together, these attributes result in significantly reduced core fissile
inventories and spent nuclear fuel mass 
\cite{gif_generation_2008,gif_generation_2015}.  
Due to these characteristics, the \gls{MSR} is potentially uniquely capable of 
burning actinides and extending fuel resources.

@@

The present work introduces the open source simulation tool, Moltres
\cite{lindsay_moltres_2017}, for simulating \glspl{MSR}.  By implementing
deterministic neutronics and thermal hydraulics in the context of the
\gls{MOOSE} finite element modeling framework, Moltres solves arbitrary-group
neutron diffusion, temperature, and precursor governing equations in anywhere
from one to three dimensions and can be deployed on an arbitrary number of
processing units. Through its computing power, Moltres is devoted to previously
unmatched fidelity in coupled neutronics and thermal hydraulics \gls{MSR}
simulation.

@@

Moltres \cite{lindsay_moltres_2017} is implemented as an application for
use atop the \gls{MOOSE} \cite{gaston_physics-based_2015} framework.
Accordingly, Moltres includes physics kernels and boundary conditions for
solving for neutron fluxes, temperature, and precursor concentrations. In \gls{MOOSE}
jargon, kernels are C++ classes that contain methods for computing residual and
Jacobian contributions corresponding to individual pieces of governing
equations. Developing the code-base in this way allows modular construction
of equation systems; e.g. the kernel used to represent heat
conduction can also represent generic chemical diffusion. Moltres
also features neutron and precursor ``actions.'' These actions automatically 
construct the systems of equations for an arbitrary number of neutron and
precursor groups. Therefore, as long as group constants are provided in an appropriate
tabular form, a user only has to modify a couple of lines in a Moltres input
file to change from say two to forty-four neutron groups.
